\huge A Usability Evaluation of Tor Launcher

### 2017-02-23 pets2017-paper/pets2017-paper.tex
Grammar fixes noticed by pets 2017.3 reviewers.

  \begin{abstract}
{
We perform the first usability test on Tor Launcher, a graphical user interface (GUI) that all Tor Browser users must use to configure their initial connection to the Tor network. Users who do not require a proxy or a non-default bridge can usually connect to connect to the Tor network with the Tor Launcher GUI. However, user observations revealed that participants were intimidated by the tasks, unsure of what to do, and likely to get stuck configuring network components that they did not need. User testing showed that most users take more than 10 minutes to connect to Tor if the public relays are censored and half of the users cannot connect to Tor if the interface's hardcoded bridges are censored. We conclude with recommendations based on what we learned and by start a discussion on alternative 
approaches to bootstrap a connection to Tor. 
}
\end{abstract}
  \keywords{Usable Security, User Studies, Tor, Security, Censorship, Anonymity}
%  \classification[PACS]{}
 % \communicated{...}
 % \dedication{...}

@@

Tor relays are the routers in the Tor network. The Tor network is a group of routers that perform onion routing, a technique for anonymous communication over a computer network.  
Guard relays that serve as an entry node into the Tor network and receive packets from the user. Middle relays forward traffic from an entry relay to an exit relay, and provide an extra layer of encryption in the Tor network. Exit relays receive traffic from a middle relay, and direct the traffic to its intended destination. 
A user uses Tor Browser to connect to the Tor network, which indirectly connects to websites.

Bridges are unlisted Tor relays that serve as an alternative entry node.
Bridges can be unlisted relays that behave similarly to a regular Tor relay,  
but most run a pluggable transport (referred to as ``transport'' for shorthand) that obfuscates traffic. 
Pre-configured bridges can be selected by ``Transport type,'' which refer to various
censorship circumvention technologies (``pluggable transports'').
Most transports rely on the secrecy of their static IP addresses for their effectiveness.
These include ``fte'' and ``fte-ipv6''~\cite{fte},
which disguise the Tor protocol as another protocol (such as HTTP), and
``obfs3''~\cite{obfs3}, ``obfs4''~\cite{obfs4}, and ``scramblesuit''~\cite{scramblesuit},
which encrypt or alter the Tor protocol to appear as random noise.
Other transports route traffic through other services and do not need secret IP address. 
``flashproxy''~\cite{flashproxy} connects through third party web browsers,
and the ``meek''~\cite{fifield2015blocking} options route traffic
through content delivery networks. Fig.~\ref{fig:old-bridge-combobox} shows the bridge and transport options at the time of the study. A user uses a bridge to connect to the Tor network while Tor relays or the Tor network protocol is being censored.

@@

\subsection{Connecting to Tor} 
A ``bridge line,'' a specifically formatted bridge specification that
includes its IP address, transport type, and other metadata 
officially configures Tor Browser to use bridges.
Users can do this more easily by choosing a 
a hard-coded option in the interface (see Figure~\ref{fig:old-bridge-combobox}) 
that select a group of bridges that use a particular transport.
For instance, choosing the hard-coded obfs3 option
configures a handful of bridges that use the obfs3 transport.
If the built-in bridges do not work, users can obtain bridge lines
through out-of-band channels~\cite{bridgedb}.

@@

We conducted our studies at <redacted>, which only had Windows machines. 
So we used Windows Firewall rules to block IP addresses of public Tor relays (E2, E3) and default bridges (E3). 
and the Windows operating system hosts file to block websites by
mapping domain names to localhost (127.0.0.1) (E1, E2, E3). For all experiments, we blocked torproject.org and its subdomains to discourage downloading Tor Browser (as we had installed a specific version on the test computers) and wikipedia.org, cnn.com, and their subdomains (these were our simulated ``censored'' websites).

@@

\subsection{Observations}
The interface did not suppose that a user has previous exposure to Tor. To help new users, it provided recommendations in the text and populated some options (such as bridges) with recommended options. However, the interface did require the user to figure out if Tor relays are blocked or if a proxy is required. And the interface did not discourage users from configuring components that are not necessary to connect to Tor. The proxy configuration has the potential for a lot of error, as there are a many free-form input fields.

More generally, we suspected that new users or infrequent users would struggle to configure bridges and proxies. We doubted that users would have an understanding of how the Internet well enough to even explain how Tor relays, bridges, and proxies worked. Additionally, as mentioned previously, Tor relays, bridges, and proxies all allow indirect connections, and the difference in terminology can be confusing. The terminology of bridges and transports are also specific to Tor, and not other censorship circumvention software.

@@

We distributed participants evenly in number across experimental conditions:  5~in E1, 5~in E2, and 6~in E3. We ensured that each condition had a participant who had used Tor Browse before, and tried for some variation in gender, age, ``technical expertise,'' and ``use of security tools'' in each experimental condition as well.

\subsection{Setup} 
We ran the experiment in a meeting room in <redacted building> at <redacted university>. The room had a desk and chair, where a monitor, keyboard, and a Windows computer were set up. On a clean computer, we manually downloaded and installed the necessary software for the experiment: Tor Browser 5.0.3 for testing, Chrome, Firefox, and Internet Explorer so that participants could browse the Internet in a another browser of their choice, and VLC to record the screen during the experiment. Before each participant entered the room, we ran a script on the computer that
set up one of the three simulated environments (E1, E2, or E3) and started recording the computer screen.

@@

We started by informing the participant of the simulated censorship environment (Appendix~\ref{qualitative-script}) and task. We explicitly stated that the they should use Tor to circumvent censorship. 
We instructed them to visit sample censored and uncensored websites
in a non-Tor browser to clarify that the Internet was functioning and
pointed out the Tor Browser shortcut on their desktop.

They were asked to complete a worksheet (Appendix~\ref{participant-worksheet}) that 
required answers from Wikipedia (censored) and CNN (uncensored).
We chose these websites because their likely familiarity~\ref{alexa}
would make the task seem less intimidating. They were given 45 minutes to complete the task. 
After instructions, researchers left to minimize interactions and watched a live feed of the participants' screen from another room.

@@

The interface uses a technical and Tor-specific terms that are unfamiliar to an average user, such as the Tor network, internet service provider (ISP), local proxy, bridges, and transports. Participants found the interface confusing, and were often unable to answer the questions that were designed to guide them (Figures~\ref{fig:old-bridge} and~\ref{fig:old-proxy}) and did not know what to do to configure bridges and proxies (Figures~\ref{fig:old-bridge-combobox} and~\ref{fig:old-proxy-yes}).

@@

The progress bar had dependencies that made it update oddly. If progress bar reached a 90\% and failed, the progress bar will remain at 0\% on the next attempt until the progress surpassed 90\%. This made many assume that their subsequent attempts were wrong.

@@

\begin{figure*}
\centering
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/NEW-first.png}
	\centering\captionsetup{width=1.5\linewidth}%
	\caption{The first screen (F). We reduced the text on the screen and clarified that configuration is for heavily censored environments. ``Configure'' leads to the proxy screen  (Figure~\ref{fig:new-proxy}.)}
	\label{fig:new-first}
\end{subfigure}
~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/NEW-proxyYES.png}
	\centering\captionsetup{width=1.5\linewidth}%
	\caption{The proxy screen (P). The interface locally detects if users need a proxy. If they need to configure one, proxy fields (same as Figure \ref{fig:old-proxy-yes}) are automatically populated.}
	\label{fig:new-proxy}
\end{subfigure}
~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/NEW-bridgeSettings.png}
	\centering\captionsetup{width=1.5\linewidth}%
	\caption{The bridge screen (B). We give users the options to connect  without a bridge (the default choice) alongside the other options. We tell users to when to choose a bridge. }
	\label{fig:new-nobridge}
\end{subfigure}
~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/NEW-bridgeSettings-default.png}
	\centering\captionsetup{width=1.5\linewidth}%
	\caption{We give a second bridge recommendation for the provided bridges. We hide the text field to input custom bridge information until they click the radio button to configure one.}
	\label{fig:new-bridge}
\end{subfigure}
~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/NEW-bridgeSettings-combobox.png}
	\centering\captionsetup{width=1.5\linewidth}%
	\caption{The provided bridges and their supporting transports remains unchanged. This dropdown menu is the same as the bridge settings in the old interface (Figure~\ref{fig:old-bridge-combobox}).}
	\label{fig:new-bridge-combobox}
\end{subfigure}
~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/NEW-bridgeHelp.png}
	\centering\captionsetup{width=1.5\linewidth}%
	\caption{The bridge help screen (BH). We did not make any changes to this page. This screen is identical to that in the old interface (Figure~\ref{fig:old-bridge-help}).}
	\label{fig:new-bridge-help}
\end{subfigure}
~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/NEW-summary.png}
	\centering\captionsetup{width=1.5\linewidth}%
	\caption{The summary screen (S). This screen shows users what they had configured in the interface. If they  configured proxies or bridges, this summarizes their choices.}
	\label{fig:new-summary}
\end{subfigure}
~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/NEW-progress.png}
	\centering\captionsetup{width=1.5\linewidth}%
	\caption{The progress bar (Pr). A checkpoint progress bar shows the status of each component in the connection (there are more checkpoints if bridges and proxies are configured).}
	\label{fig:new-progress}
\end{subfigure}
\caption{
A redesigned version of the Tor Browser 5.0.3 Tor Launcher GUI. Screens are in the order that they appear. 
}
\label{fig:new-interface}
\end{figure*}

@@

To help users decide what to do, we label the configure button as an option heavily censored environments, tell users to configure a bridge if Tor is censored, and give a secondary bridge recommendation.

To help users understand, we added a summary screen displays the current bridge and proxy settings, switched proxy and bridge screens to put them in a topologically sequential order (Figure~\ref{fig:topology}), and added checklist indicators into the progress bar to that show if various components were reached.

@@

\subsection{Setup}
We ran our experiment at <redacted lab>, an experimental social science laboratory for behavioral experiments. The testing room had 36 workstations with identical Windows~7 laptops. Side panels at each workstation to discouraged participants from looking at other screens. 
%Xlab~\cite{xlab}, the Experimental Social Science Laboratory at the University of California, Berkeley. 
The computers at <Redacted lab> use a system restore software to revert computers to a clean version at the beginning of each session.

@@

\subsection{Procedure}
We assigned participants  to a simulated censorship environment combination at random by being assigning them to a computer at random. We told the participants the purpose of the study, what data was collected, and any associated risks. Then they signed a consent form with this information in writing. Before the experiment, we clarified that they could stop at any time during the experiment with no negative consequences.

@@

\begin{figure}[t]
\centering
\includegraphics{time_to_success_active_clamped}
\caption{
Only a small fraction of the time was used to configure bridges and proxies.
Non-finishing participants' active time was computed by
subtracting the amount of time spent on the progress screen from the 
their assigned completion time of 40:08.
}
\label{fig:time_to_success_active_clamped}
\end{figure}

%things to keep in mind
We believe that configuration time is a meaningful metric because 1) bootstrapping can dominate measurements for users do not need much time to configure their connection (E1 participants), and 2) many errors do not interrupt the connection attempt and cause many users to wait a long time before they manually cancel the connection to try again. This is metric is not perfect though, since it does not reflect how some participants actively searched for help in another browser rather than passively waiting for their connections to work.

@@

\subsection{Usability of Tor Launcher} 
We confirmed our observations from our qualitative user test and find that participants wait the progress screen for a long time, spend time configuring proxies when they did not need to, and do not know what to do if the recommended bridge doesn't work.

From our measurements, we find that 63\% (72 of 114) of first attempts to connect failed and 79\% (363 of 458) of total attempts to connect failed. Users average over 3 minutes if they needed a bridge and averaging over 20 minutes if they needed a meek or custom bridge.

Ideally, almost all users should be able to configure the necessary or optional network components and connect to Tor within a few minutes. Neither the Tor Browser's 5.0.3 Tor Launcher GUI or our redesigned Tor Launcher GUI meets this goal.

@@

While we believe that adopting our design faithfully will save users time. But since we did not test our design changes independently, we cannot (and do not) claim the effects each change. Alternative designs may be better solutions.

@@

\section{Related Work}
\label{sec:related} 
% intro to usable security 
The difference between a poor interface and a good interface can influence users’ ability to perform tasks securely~\cite{payne2008brief}. Usable security aims to improve the security of a system by designing with the user in mind. This involves informing users about the system, communicating risks in a way that is understandable, clarifying what the security requirements are, and providing guidance with technical tasks~\cite{adams1999users}. Our work contributes to the body of usable security by evaluating Tor Browser, which is an anonymity and censorship circumvention software that requires user interaction. Other usable security research explores on a variety of security software or features, such as email encryption software ~\cite{whitten1999johnny}\cite{garfinkel2005johnny}, authentication methods~\cite{morris1979password}\cite{dhamija2000deja}\cite{suo2005graphical}, web indicators~\cite{dhamija2006phishing}\cite{akhawe2013alice}, and security warnings ~\cite{schechter2007emperor}\cite{egelman2008you}.

@@

We used usability lab studies (one-on-one experiments with a given a set of scenarios and tasks for a specific use of  a product or service) and usability benchmarking (tightly scripted usability studies are performed with many participants used to collect measures of performance) to get qualitative and quantitative behavioral data about Tor Launcher's GUI~\cite{krol2016towards}. There are other ways to collect behavioral data as well, such as eye tracking, clickstream analysis and AB testing. These are in contrast with a variety of user experience research methods that collect qualitative or quantitative attitudinal data, such as focus group, camera studies, and product surveys~\cite{ux-methods}. We performed interviews after our lab study, but we mostly used these interviews to verify our behavioral observations rather than to draw conclusions about what people thought about their experience.

@@

% Previous Tor studies 
Our work uniquely contributes to Tor by examining the usability of the configuration interface.  
Previous usability studies on Tor have focused on installation and use. Norcie et~al.~\cite{norcie2012eliminating} performed a 25-user test of Tor Browser and found that 64\% of users were unable complete installation or browsing tasks. Fabian et~al.~\cite{fabian2010privately} discussed how added latency benefits anonymity~\cite{dingledine2009performance} but reduces usability. They quantified how the difference in latency causes frustration and decreases adoption. Clark et~al.~\cite{clark2007usability} performed a cognitive walkthrough of Tor Browser deployment options (Vidalia, Privoxy, Torbutton, and FoxyProxy) and found that none were satisfactory from a usability perspective. They highlight the best aspects of each tool and offer usability improvements. We do not know of any published usability evaluations of
Tor Browser the 3.5 series in 2013, which introduced radical UI changes~\cite{torbrowser-35}.
Lee and Fifield~\cite{uxsprint} ran an informal UX sprint that recruited 5 users to install and use Tor Browser to observe their behavior. This uncovered some usability issues~\cite{uxsprint2015-tickets} and caused UI changes in Tor Browser version~4.5.

\section{Conclusion} 
\label{sec:conclusion}
We believe that an interface is usable if a new user can to identify what to do, knows if and when they do the right thing in the process, and can accomplish the required tasks. Tor Browser 5.0.3's configuration interface does not meet these requirements. We qualified where the interface is not usable with user observations and quantified how unusable the interface is with user interaction logs. We believe that our recommended changes will will help users connect to Tor in censored environments, but encourage discussion about alternative ways to configure a connection that would be easier for users.

@@

%P5 (has used tor before): E3 (22:06; 0:00 to 22:06)
\pquote{P16 (previous Tor user, custom bridge, 22:06)}{They tried and retried connecting directly, then they tried connecting with the recommended bridge. After briefly looking at error messages the system log, they retried connecting directly two more times. After trying to configure a proxy for a while, they instead decided not to use one and tried connecting with a meek-google bridge, which would have worked. But  due to a bug in the progress bar that prevents it from updating correctly on subsequent attempts, they gave up before it could connect. They made a connection with the custom bridge by following the instructions from the bridge help button (they created a throwaway email account, emailed the bridge responder with poor syntax and did not get a response, emailed the bridge responder again with correct syntax and got a response, and then typed in the bridge information into the custom bridge field).}

>>>>

  \begin{abstract}
{
We perform the first usability test on Tor Launcher, a graphical user interface (GUI) that all Tor Browser users must use to configure their initial connection to the Tor network. Users who do not require a proxy or a non-default bridge can usually connect to the Tor network with the Tor Launcher GUI. However, user observations revealed that participants were intimidated by the tasks, unsure of what to do, and likely to get stuck configuring network components that they did not need. User testing showed that most users take more than 10 minutes to connect to Tor if the public relays are censored and half of the users cannot connect to Tor if the interface's hardcoded bridges are censored. We conclude with recommendations based on what we learned and start a discussion on alternative 
approaches to bootstrap a connection to Tor. 
}
\end{abstract}
  \keywords{Usable Security, User Studies, Tor, Security, Censorship, Anonymity}
%  \classification[PACS]{}
 % \communicated{...}
 % \dedication{...}

@@

Tor relays are the routers in the Tor network. The Tor network is a group of routers that perform onion routing, a technique for anonymous communication over a computer network.  
Guard relays serve as an entry node into the Tor network and receive packets from the user. Middle relays forward traffic from an entry relay to an exit relay, and provide an extra layer of encryption in the Tor network. Exit relays receive traffic from a middle relay, and direct the traffic to its intended destination. 
A user uses Tor Browser to connect to the Tor network, which indirectly connects to websites.

Bridges are unlisted Tor relays that serve as an alternative entry node.
Bridges can be unlisted relays that behave similarly to a regular Tor relay,  
but most run a pluggable transport (referred to as ``transport'' for shorthand) that obfuscates traffic. 
Pre-configured bridges can be selected by ``Transport type,'' which refer to various
censorship circumvention technologies (``pluggable transports'').
Most transports rely on the secrecy of their static IP addresses for their effectiveness.
These include ``fte'' and ``fte-ipv6''~\cite{fte},
which disguise the Tor protocol as another protocol (such as HTTP), and
``obfs3''~\cite{obfs3}, ``obfs4''~\cite{obfs4}, and ``scramblesuit''~\cite{scramblesuit},
which encrypt or alter the Tor protocol to appear as random noise.
Other transports route traffic through other services and do not need a secret IP address. 
``flashproxy''~\cite{flashproxy} connects through third party web browsers,
and the ``meek''~\cite{fifield2015blocking} options route traffic
through content delivery networks. Fig.~\ref{fig:old-bridge-combobox} shows the bridge and transport options at the time of the study. A user uses a bridge to connect to the Tor network while Tor relays or the Tor network protocol is being censored.

@@

\subsection{Connecting to Tor} 
A ``bridge line,'' a specifically formatted bridge specification that
includes its IP address, transport type, and other metadata 
officially configures Tor Browser to use bridges.
Users can do this more easily by choosing
a hard-coded option in the interface (see Figure~\ref{fig:old-bridge-combobox}) 
that select a group of bridges that use a particular transport.
For instance, choosing the hard-coded obfs3 option
configures a handful of bridges that use the obfs3 transport.
If the built-in bridges do not work, users can obtain bridge lines
through out-of-band channels~\cite{bridgedb}.

@@

We conducted our studies at <redacted>, which only had Windows machines. 
So we used Windows Firewall rules to block the IP addresses of public Tor relays (E2, E3) and default bridges (E3),
and the Windows operating system hosts file to block websites by
mapping domain names to localhost (127.0.0.1) (E1, E2, E3). For all experiments, we blocked torproject.org and its subdomains to discourage downloading Tor Browser (as we had installed a specific version on the test computers) and wikipedia.org, cnn.com, and their subdomains (these were our simulated ``censored'' websites).

@@

\subsection{Observations}
The interface did not suppose that a user has previous exposure to Tor. To help new users, it provided recommendations in the text and populated some options (such as bridges) with recommended options. However, the interface did require the user to figure out if Tor relays are blocked or if a proxy is required. And the interface did not discourage users from configuring components that are not necessary to connect to Tor. The proxy configuration has the potential for a lot of error, as there are many free-form input fields.

More generally, we suspected that new users or infrequent users would struggle to configure bridges and proxies. We doubted that users would understand the Internet well enough to even explain how Tor relays, bridges, and proxies worked. Additionally, as mentioned previously, Tor relays, bridges, and proxies all allow indirect connections, and the difference in terminology can be confusing. The terminology of bridges and transports are also specific to Tor, and not other censorship circumvention software.

@@

We distributed participants evenly in number across experimental conditions:  5~in E1, 5~in E2, and 6~in E3. We ensured that each condition had a participant who had used Tor Browser before, and tried for some variation in gender, age, ``technical expertise,'' and ``use of security tools'' in each experimental condition as well.

\subsection{Setup} 
We ran the experiment in a meeting room in <redacted building> at <redacted university>. The room had a desk and chair, where a monitor, keyboard, and a Windows computer were set up. On a clean computer, we manually downloaded and installed the necessary software for the experiment: Tor Browser 5.0.3 for testing, Chrome, Firefox, and Internet Explorer so that participants could browse the Internet in another browser of their choice, and VLC to record the screen during the experiment. Before each participant entered the room, we ran a script on the computer that
set up one of the three simulated environments (E1, E2, or E3) and started recording the computer screen.

@@

We started by informing the participant of the simulated censorship environment (Appendix~\ref{qualitative-script}) and task. We explicitly stated that they should use Tor to circumvent censorship. 
We instructed them to visit sample censored and uncensored websites
in a non-Tor browser to clarify that the Internet was functioning and
pointed out the Tor Browser shortcut on their desktop.

They were asked to complete a worksheet (Appendix~\ref{participant-worksheet}) that 
required answers from Wikipedia (censored) and CNN (uncensored).
We chose these websites because their likely familiarity~\cite{alexa}
would make the task seem less intimidating. They were given 45 minutes to complete the task. 
After instructions, researchers left to minimize interactions and watched a live feed of the participants' screen from another room.

@@

The interface uses technical and Tor-specific terms that are unfamiliar to an average user, such as the Tor network, internet service provider (ISP), local proxy, bridges, and transports. Participants found the interface confusing, and were often unable to answer the questions that were designed to guide them (Figures~\ref{fig:old-bridge} and~\ref{fig:old-proxy}) and did not know what to do to configure bridges and proxies (Figures~\ref{fig:old-bridge-combobox} and~\ref{fig:old-proxy-yes}).

@@

The progress bar had dependencies that made it update oddly. If progress bar reached 90\% and failed, the progress bar will remain at 0\% on the next attempt until the progress surpassed 90\%. This made many assume that their subsequent attempts were wrong.

@@

\begin{figure*}
\centering
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/NEW-first.png}
	\centering\captionsetup{width=1.5\linewidth}%
	\caption{The first screen (F). We reduced the text on the screen and clarified that configuration is for heavily censored environments. ``Configure'' leads to the proxy screen  (Figure~\ref{fig:new-proxy}.)}
	\label{fig:new-first}
\end{subfigure}
~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/NEW-proxyYES.png}
	\centering\captionsetup{width=1.5\linewidth}%
	\caption{The proxy screen (P). The interface locally detects if users need a proxy. If they need to configure one, proxy fields (same as Figure \ref{fig:old-proxy-yes}) are automatically populated.}
	\label{fig:new-proxy}
\end{subfigure}
~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/NEW-bridgeSettings.png}
	\centering\captionsetup{width=1.5\linewidth}%
	\caption{The bridge screen (B). We give users the options to connect  without a bridge (the default choice) alongside the other options. We tell users when to choose a bridge. }
	\label{fig:new-nobridge}
\end{subfigure}
~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/NEW-bridgeSettings-default.png}
	\centering\captionsetup{width=1.5\linewidth}%
	\caption{We give a second bridge recommendation for the provided bridges. We hide the text field to input custom bridge information until they click the radio button to configure one.}
	\label{fig:new-bridge}
\end{subfigure}
~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/NEW-bridgeSettings-combobox.png}
	\centering\captionsetup{width=1.5\linewidth}%
	\caption{The provided bridges and their supporting transports remains unchanged. This dropdown menu is the same as the bridge settings in the old interface (Figure~\ref{fig:old-bridge-combobox}).}
	\label{fig:new-bridge-combobox}
\end{subfigure}
~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/NEW-bridgeHelp.png}
	\centering\captionsetup{width=1.5\linewidth}%
	\caption{The bridge help screen (BH). We did not make any changes to this page. This screen is identical to that in the old interface (Figure~\ref{fig:old-bridge-help}).}
	\label{fig:new-bridge-help}
\end{subfigure}
~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/NEW-summary.png}
	\centering\captionsetup{width=1.5\linewidth}%
	\caption{The summary screen (S). This screen shows users what they had configured in the interface. If they  configured proxies or bridges, this summarizes their choices.}
	\label{fig:new-summary}
\end{subfigure}
~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/NEW-progress.png}
	\centering\captionsetup{width=1.5\linewidth}%
	\caption{The progress bar (Pr). A checkpoint progress bar shows the status of each component in the connection (there are more checkpoints if bridges and proxies are configured).}
	\label{fig:new-progress}
\end{subfigure}
\caption{
A redesigned version of the Tor Browser 5.0.3 Tor Launcher GUI. Screens are in the order that they appear. 
}
\label{fig:new-interface}
\end{figure*}

@@

To help users decide what to do, we label the configure button as an option for heavily censored environments, tell users to configure a bridge if Tor is censored, and give a secondary bridge recommendation.

To help users understand, we added a summary screen displaying the current bridge and proxy settings, switched proxy and bridge screens to put them in a topologically sequential order (Figure~\ref{fig:topology}), and added checklist indicators into the progress bar that show if various components were reached.

@@

\subsection{Setup}
We ran our experiment at <redacted lab>, an experimental social science laboratory for behavioral experiments. The testing room had 36 workstations with identical Windows~7 laptops. Side panels at each workstation discouraged participants from looking at other screens. 
%Xlab~\cite{xlab}, the Experimental Social Science Laboratory at the University of California, Berkeley. 
The computers at <Redacted lab> use a system restore software to revert computers to a clean version at the beginning of each session.

@@

\subsection{Procedure}
We assigned participants  to a simulated censorship environment combination at random by assigning them to a computer at random. We told the participants the purpose of the study, what data was collected, and any associated risks. Then they signed a consent form with this information in writing. Before the experiment, we clarified that they could stop at any time during the experiment with no negative consequences.

@@

\begin{figure}[t]
\centering
\includegraphics{time_to_success_active_clamped}
\caption{
Only a small fraction of the time was used to configure bridges and proxies.
Non-finishing participants' active time was computed by
subtracting the amount of time spent on the progress screen from
their assigned completion time of 40:08.
}
\label{fig:time_to_success_active_clamped}
\end{figure}

%things to keep in mind
We believe that configuration time is a meaningful metric because 1) bootstrapping can dominate measurements for users who do not need much time to configure their connection (E1 participants), and 2) many errors do not interrupt the connection attempt and cause many users to wait a long time before they manually cancel the connection to try again. This metric is not perfect though, since it does not reflect how some participants actively searched for help in another browser rather than passively waiting for their connections to work.

@@

\subsection{Usability of Tor Launcher} 
We confirmed our observations from our qualitative user test and find that participants wait on the progress screen for a long time, spend time configuring proxies when they did not need to, and do not know what to do if the recommended bridge doesn't work.

From our measurements, we find that 63\% (72 of 114) of first attempts to connect failed and 79\% (363 of 458) of total attempts to connect failed. Users average over 3 minutes if they needed a bridge and are averaging over 20 minutes if they needed a meek or custom bridge.

Ideally, almost all users should be able to configure the necessary or optional network components and connect to Tor within a few minutes. Neither the Tor Browser's 5.0.3 Tor Launcher GUI nor our redesigned Tor Launcher GUI meets this goal.

@@

While we believe that adopting our design faithfully will save users time. But since we did not test our design changes independently, we cannot (and do not) claim specific effects for each change. Alternative designs may be better solutions.

@@

\section{Related Work}
\label{sec:related} 
% intro to usable security 
The difference between a poor interface and a good interface can influence users’ ability to perform tasks securely~\cite{payne2008brief}. Usable security aims to improve the security of a system by designing with the user in mind. This involves informing users about the system, communicating risks in a way that is understandable, clarifying what the security requirements are, and providing guidance with technical tasks~\cite{adams1999users}. Our work contributes to the body of usable security by evaluating Tor Browser, which is an anonymity and censorship circumvention software that requires user interaction. Other usable security research explores a variety of security software or features, such as email encryption software ~\cite{whitten1999johnny}\cite{garfinkel2005johnny}, authentication methods~\cite{morris1979password}\cite{dhamija2000deja}\cite{suo2005graphical}, web indicators~\cite{dhamija2006phishing}\cite{akhawe2013alice}, and security warnings ~\cite{schechter2007emperor}\cite{egelman2008you}.

@@

We used usability lab studies (one-on-one experiments with a given set of scenarios and tasks for a specific use of  a product or service) and usability benchmarking (tightly scripted usability studies are performed with many participants used to collect measures of performance) to get qualitative and quantitative behavioral data about Tor Launcher's GUI~\cite{krol2016towards}. There are other ways to collect behavioral data as well, such as eye tracking, clickstream analysis and AB testing. These are in contrast with a variety of user experience research methods that collect qualitative or quantitative attitudinal data, such as focus group, camera studies, and product surveys~\cite{ux-methods}. We performed interviews after our lab study, but we mostly used these interviews to verify our behavioral observations rather than to draw conclusions about what people thought about their experience.

@@

% Previous Tor studies 
Our work uniquely contributes to Tor by examining the usability of the configuration interface.  
Previous usability studies on Tor have focused on installation and use. Norcie et~al.~\cite{norcie2012eliminating} performed a 25-user test of Tor Browser and found that 64\% of users were unable to complete installation or browsing tasks. Fabian et~al.~\cite{fabian2010privately} discussed how added latency benefits anonymity~\cite{dingledine2009performance} but reduces usability. They quantified how the difference in latency causes frustration and decreases adoption. Clark et~al.~\cite{clark2007usability} performed a cognitive walkthrough of Tor Browser deployment options (Vidalia, Privoxy, Torbutton, and FoxyProxy) and found that none were satisfactory from a usability perspective. They highlight the best aspects of each tool and offer usability improvements. We do not know of any published usability evaluations of
Tor Browser since the 3.5 series in 2013, which introduced radical UI changes~\cite{torbrowser-35}.
Lee and Fifield~\cite{uxsprint} ran an informal UX sprint that recruited 5 users to install and use Tor Browser to observe their behavior. This uncovered some usability issues~\cite{uxsprint2015-tickets} and caused UI changes in Tor Browser version~4.5.

\section{Conclusion} 
\label{sec:conclusion}
We believe that an interface is usable if a new user can identify what to do, knows if and when they do the right thing in the process, and can accomplish the required tasks. Tor Browser 5.0.3's configuration interface does not meet these requirements. We qualified where the interface is not usable with user observations and quantified how unusable the interface is with user interaction logs. We believe that our recommended changes will will help users connect to Tor in censored environments, but encourage discussion about alternative ways to configure a connection that would be easier for users.

@@

%P5 (has used tor before): E3 (22:06; 0:00 to 22:06)
\pquote{P16 (previous Tor user, custom bridge, 22:06)}{They tried and retried connecting directly, then they tried connecting with the recommended bridge. After briefly looking at error messages in the system log, they retried connecting directly two more times. After trying to configure a proxy for a while, they instead decided not to use one and tried connecting with a meek-google bridge, which would have worked. But  due to a bug in the progress bar that prevents it from updating correctly on subsequent attempts, they gave up before it could connect. They made a connection with the custom bridge by following the instructions from the bridge help button (they created a throwaway email account, emailed the bridge responder with poor syntax and did not get a response, emailed the bridge responder again with correct syntax and got a response, and then typed in the bridge information into the custom bridge field).}
